\chapter{\centering Project Description and Motivation} % Main chapter title

\label{Chapter Project Description} % Change X to a consecutive number; for referencing this 
% chapter elsewhere, use \ref{ChapterX}

Nowadays, time management apps such as Outlook, Google Calendar,etc have proven to be an essential tool in our modern day business and personal lives.

However, the problem with most of these apps is that they require you to have a constant internet connection to use their application. In addition,
the data that you will generate while using these apps belongs to big tech corporations with no clear or transparent way to export it
or to view them outside the app once they are created. These factors along with the fact that the majority of these apps are proprietary 
products mean that they are not an ideal choice for privacy oriented users.

% This is where our project, the time scheduler is born. By combining our Java, database knowledge, and GUI skills we managed to build an app with modern day UI looks that has the ability to create accounts for users and save their information in their locally in their computer. The data store in the computer is only 
% backup in our database if the user choose to do so. In the case that they do, we provide full login, sign up
% functionalities that allow them to continue their work on any machine.

Data protection is a key aspect of our application design. This is why the user's data is backed up in our remote database 
only if they choose to do so by logging in with an existing account or if they sign up for a new account. Otherwise, if they do not want 
their data to be stored in our local database, they can choose to use the offline mode, where all of their data is stored and used locally
on their computer. Both methods have their own way to transfer the data onto another machine allowing the user to be more flexible.  

The main page of the app was designed to offer a modern up-to-date UI that suits the current standards of UI design. Each events and dates 
are color coded in vibrant colors based on their priority so that color blind users can still interact with the app. 

Users are able to create, schedule, edit and delete events, and furthermore invite other users to their event. In addition, our app contains an email function where the users will be reminded to their upcoming event based on the timer option they chose as well as receive emails on upcoming changes or cancellation of event(s) that they are involved in. 

% As mentioned above, privacy is a key feature that we wanted to consider so the data that is generated while using our app can always be exported to either a .txt or database file that can be imported back into the app for later usage. In addition to this, our app can be entirely used without the need for
% any internet connection by using our integrated offline mode.

What is yours will always rightfully belong to you!